Deciphering Key Determinants of Biden Voter Support: Insights from Logistic Regression Analysis in the 2020 US Presidential Election

### 2024-03-17 paper/paper.qmd
done reuslts

```{r}
#| warning: false
#| echo: false
#| label: raw_data
#| tbl-cap: A sample of CES 2020 survey data.

@@

# model summary
modelsummary::modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
)
```

**Gender**: Test

**Education**: Test

**Race**: Test

**Age**:  Test

>>>>

```{r}
#| echo: false
#| label: raw_data
#| tbl-cap: A sample of CES 2020 survey data.

@@

# model summary
modelsummary::modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
)
```
As a note, the standard error for any value discussed below shall be abbreviated as sd-err.

**Gender**: The coefficient for Males is -0.45 (0.051 sd-err) which means Males are less likely to cast a vote for Biden compared to Females, or that Males would choose Trump in an election, given that Trump and Biden were the only candidates to choose from.

**Education**: We see that with an increase in literacy level, the likelihood that a candidate will vote for Biden increases. Observe that as we move upwards in the following list of categories: High school graduate, some college, 2-year, 4-year and post-grad, we see that the corresponding coefficients are -0.267 (sd-err 0.198), 0.054 (sd-err 0.195), 0.095 (sd-err 0.203), 0.445 (sd-err 0.196) and 0.906 (sd-err 0.199) respectively, meaning that the more educated a candidate is, the more likely they are to vote for Biden.

**Race**: Amongst the positive coefficients, observe that voters identifying on the survey as Black demonstrate the highest support for Biden amongst all other racial groups of respondents with a coefficient of 2.590 (sd-err 0.155), whereas Hispanic and Asian respondents bear coefficients 0.572 (sd-err 0.905) and 0.635 (sd-err 0.162) respectively. Coming in last place, we have Middle Eastern respondents with the smallest positive coefficient compared to the other racial groups, with a value of 0.356 (sd-err 0.181). Finally, we have respondents identifying with "Two or more races" that are actually LESS likely to support Biden, with a value of -0.294 (sd-err 0.172). Finally, we observe that respondents identifying as "Other" demonstrate a coefficient of 1.301, although with a comparatively higher standard error of 1.277.

**Age**: We see a coefficient value of -0.018 (sd-err 0.002) showing a weak negative correlation between the age of a respondent and whether they voted for Biden. All in all, it is bold to claim that there exists a definite negative correlation between a voter's age and whether they voted for Biden.
